Approximation as Differentiation notes

### 2025-02-10 notes.tex
Functors -> FunCat.
LatGal.

Some notes on the key constructions:
\begin{itemize}
\item Categories of families, special case of Grothendieck construction
\end{itemize}

@@

\noindent Equivalently, $\Fam(I,C)$ is the functor category $\Functors{I}{C}$.

@@

>>>>

Some notes on the key constructions:
\begin{itemize}
\item Category of families $\Fam$
\item Category of bounded lattices and Galois connections
\end{itemize}

@@

\noindent Equivalently, $\Fam(I,C)$ is the functor category $\FunCat{I}{C}$.

@@

\noindent \todo{Some properties of $\Fam(C)$.}

\subsection{Category of bounded lattices and Galois connections}

Define the category $\LatGal$ where:
\begin{itemize}
\item objects $L$ are bounded lattices;
\item morphisms $(f, g)$ from $L$ to $L'$ are meet-semilattice homomorphisms $f: L \to L'$ paired with
join-semilattice homomorphisms $g: L' \to L$ satisfying $y \leq fx \iff gy \leq x$.
\end{itemize}

\noindent \note{The Agda defines an object of $\LatGal$ as a set equipped with meet- and join-semilattice
structures but there is no requirement that they satisfy the absorption laws or induce the same partial
order.}
